### 2011-04-01 article_basics_content.tex
Moved files to papers directory.

\subsection{GTK+}

\subsubsection{A kód}

\vspace{16pt}
\fontsize{6pt}{6pt}
\begin{verbatim}
  1 #include <gtk/gtk.h>
  2
  3 static void hello( GtkWidget *widget,
  4                    gpointer   data )
  5 {
  6   g_print ("%s\n", (const char *) data);
  7 }
  8
  9 static gboolean delete_event( GtkWidget *widget,
 10                               GdkEvent  *event,
 11                               gpointer   data )
 12 {
 13   g_print ("delete event occurred\n");
 14
 15   return TRUE;
 16 }
 17
 18 static void destroy( GtkWidget *widget,
 19                      gpointer   data )
 20 {
 21     gtk_main_quit ();
 22 }
 23
 24 int main( int   argc,
 25           char *argv[] )
 26 {
 27   GtkWidget *window;
 28   GtkWidget *button;
 29
 30   gtk_init (&argc, &argv);
 31
 32   window = gtk_window_new (GTK_WINDOW_TOPLEVEL);
 33
 34   g_signal_connect (G_OBJECT (window), "delete_event",
 35                     G_CALLBACK (delete_event), NULL);
 36
 37   g_signal_connect (G_OBJECT (window), "destroy",
 38                     G_CALLBACK (destroy), NULL);
 39
 40   gtk_container_set_border_width (GTK_CONTAINER (window), 10);
 41
 42   button = gtk_button_new_with_label ("Helló Világ");
 43
 44   g_signal_connect (G_OBJECT (button), "clicked",
 45                     G_CALLBACK (hello), NULL);
 46
 47   g_signal_connect_swapped (G_OBJECT (button), "clicked",
 48                             G_CALLBACK (gtk_widget_destroy),
 49                             G_OBJECT (window));
 50
 51   gtk_container_add (GTK_CONTAINER (window), button);
 52
 53   gtk_widget_show (button);
 54   gtk_widget_show (window);
 55
 56   gtk_main ();
 57
 58   return 0;
 59 }
\end{verbatim}

\subsubsection{Részletek sorról sorra}

@@

\subsection{gtkmm}

\subsubsection{A kód}

\vspace{16pt}
\fontsize{6pt}{6pt}
\begin{verbatim}
  1 #include <gtkmm.h>
  2 #include <iostream>
  3 
  4 static void hello(const Glib::ustring &hello_msg)
  5 {
  6   std::cout << hello_msg << std::endl;
  7 }
  8 
  9 class MyWindow : public Gtk::Window
 10 {
 11 private:
 12   Gtk::Button button;
 13 
 14 protected:
 15   virtual bool on_delete_event(GdkEventAny *event)
 16   {
 17     std::cout << "delete event occurred" << std::endl;
 18 
 19     return true;
 20   }
 21 
 22   void on_button_clicked()
 23   {
 24     Gtk::Main::quit();
 25   }
 26 
 27 public:
 28   MyWindow() :
 29     button("Helló Világ")
 30   {
 31     button.signal_clicked().connect(sigc::bind(sigc::ptr_fun(hello), "Helló Világ"));
 32     button.signal_clicked().connect(sigc::mem_fun(*this, &MyWindow::on_button_clicked));
 33 
 34     add(button);
 35 
 36     button.show();
 37   }
 38 };
 39 
 40 int main(int argc,
 41          char *argv[])
 42 {
 43   Gtk::Main kit(argc, argv);
 44 
 45   MyWindow window;
 46 
 47   Gtk::Main::run(window);
 48 
 49   return 0;
 50 }
\end{verbatim}

\subsubsection{Részletek sorról sorra}

>>>>

\subsection{A kód}

\lstinputsources
{sources/gtk_signal.c}
{sources/gtkmm_signal.cc}
{Minimál példa \textit{GtkWindow}hoz}
{lst:gtksignal}

\subsubsection{\textit{GTK+} részletek sorról sorra}

@@

\subsubsection{\textit{Gtkmm} részletek sorról sorra}

### 2011-04-01 article_concept_content.tex
Moved files to papers directory.

\vspace{16pt}
\fontsize{8pt}{8pt}
\begin{verbatim}
1  #include <gtk/gtk.h>                             #include <gtkmm.h>
2
3  int main(int argc, char *argv[])                 int main(int argc, char *argv[])
4  {                                                {
5    GtkWidget *window;
6
7    gtk_init (&argc, &argv);                         Gtk::Main kit(argc, argv);
8
9    window = gtk_window_new (GTK_WINDOW_TOPLEVEL);   Gtk::Window window;
10   gtk_widget_show  (window);
11
12   gtk_main ();                                     Gtk::Main::run(window);
13
14   return 0;                                        return 0;
15 }                                                }
\end{verbatim}

>>>>

\lstinputsources
{sources/window_minimal.c}
{sources/window_minimal.cc}
{Minimálisan szükséges kód \textit{GTK+}/\textit{gtkmm} használatához}
{lst:windowminimal}
